---
title: 'Analyzing ToothGrow dataset'
author: "Gastón Tognola"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

# Part 2: Basic Inferential Data Analysis Instructions

## Instructions
Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

1. Load the ToothGrowth data and perform some basic exploratory data analyses
2. Provide a basic summary of the data.
3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4. State your conclusions and the assumptions needed for your conclusions.

## 1. Loading dataset and exploratory analysis
```{r}
library(ggplot2)
data(ToothGrowth)
head(ToothGrowth)
```


```{r, echo=FALSE}
data = ToothGrowth
ggplot(data = data, aes(x = supp, y = len, color = factor(dose)) ) + geom_boxplot() + xlab("Supplement type") + ylab("Length") + scale_color_discrete(name = "Dose")
```

## 2. Data summary




